Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-11-26 2_revisions/V4_ITT_minor_revision/0_manuscript_blind/itt-emotion_blind.tex
Added to revisions folder

    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}, where it is stated that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others. These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}. In each of these dimensions, at least one element of service expectations were found to be significantly different for countries grouped under contrasting attributes (e.g. individualistic countries vs collectivist countries, high uncertainty avoidance countries vs low uncertainty avoidance countries). Although Hofstede's typology, particularly the fifth dimension, which was added with the alternate name \textit{Confucian dynamic}, has received criticism from academics with a Chinese background for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}. Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions . The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}. This avoids making the assumption that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes. Gender stereotypes such as these have also been subject of critique for Hofstede's model\cite[][]{jeknic2014gender}. Our study is in agreement with these critiques, and therefore will avoid considering these for our discussion.

>>>>

    In \cite{donthu1998cultural}, subjects from 10 different countries were compared in their expectations of service quality and analyzed through the lens of Hofstede's typology of culture \cite[][]{hofstede1984culture}, where it is stated that although culture has no one specific index, five dimensions of culture can be used to analyze or categorize a country in comparison to others. These are \textit{power distance}, \textit{uncertainty avoidance}, \textit{individualism-collectivism}, \textit{masculinity-femininity}, and \textit{long-term versus short-term orientation}. In each of these dimensions, at least one element of service expectations were found to be significantly different for countries grouped under contrasting attributes (e.g. individualistic countries vs collectivist countries, high uncertainty avoidance countries vs low uncertainty avoidance countries). Although Hofstede's typology, particularly the fifth dimension, which was added with the alternate name \textit{Confucian dynamic}, has received criticism from academics with a Chinese background for being misinformed on the philosophical aspects of Confucianism, as well as being a difficult dimension to measure \cite[][]{fang2003critique}. Other models, such as the GLOBE model, also take issue with some of Hofstede's dimensions and replace them with others, making a total of 9 dimensions \cite[][]{house1999cultural}. The \textit{masculinity-femininity} dimension, for example, is proposed to be instead two dimensions: \textit{gender egalitarianism} and \textit{assertiveness}. This avoids making the assumption that assertiveness is either masculine or feminine, which stems from outdated gender stereotypes. Gender stereotypes such as these have also been subject of critique for Hofstede's model\cite[][]{jeknic2014gender}. Our study is in agreement with these critiques, and therefore will avoid considering these for our discussion.

### 2020-11-26 2_revisions/V4_ITT_minor_revision/1_manuscript/itt-emotion_V3.tex
Added to revisions folder

        \author{REDACTED}

        \authorrunning{REDACTED}

        \institute{REDACTED}

@@

  REDACTED

>>>>

        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
                Hirofumi Nonaka                                                 \protect\affmark[1] \and
                Toru Hiraoka                                                    \protect\affmark[2]
        }

        \authorrunning{E. Alemán Carreón et al.}

        \institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
                    \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
                    % Corresponding Author %  \\
                    % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
                \and
                    \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{mendoza.espana@gmail.com}
                \and
                    \hspace*{1em} Hirofumi Nonaka \at
                    % Nagaoka University of Technology, Nagaoka, Japan \\
                    \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
                \and
                    \hspace*{1em} Toru Hiraoka \at
                    % University of Nagasaki, Nagasaki, Japan \\
                    \hspace*{1em} \email{hiraoka@sun.ac.jp}
                \and
                    \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
                \and
                    \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
        }

@@

  During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the data's interpretation. We would like to show gratitude to Mr. Liangyuan Zhou, Ms. Min Fan, and Ms. Eerdengqiqige for this.

  We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.

  \medskip

  Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).

  \medskip

  Conflict of interest: none
